prostate

### 2023-04-05 analyses/optimProstate.Rmd
cleanedUpCode

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_prostate<-T
#source_python('src/getSUP.py')
source_python("src/cIndex.py")
#source_python("src/dsmScript.py")
#source_python('src/deephitter.py')
##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r prostatePrep,eval=FALSE,hide=FALSE}

@@

#saveRDS(res$test,"prostateTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"prostateCV.rds")

@@

```{r setFixedHyperparameters,eval=FALSE,hide=FALSE}

klist<-readRDS("prostateCV.rds")

# 
# lr=c(0.001,0.0005)
# drpt=c(0.25,0.1)
# layer1=c(20,50,100)
# layer2=c(25,50)
# nBatch=c(100,500,1000)
# actv=c("relu","linear")#
# alp=c(0.5)

@@

#curl -d "support done" ntfy.sh/updatejykiscripts
```

```{r hyperOpDsurv,eval=FALSE,hide=FALSE}

optimDeepSurv<-function(klist,test,baselineTrials,lr,drpt,layer1,layer2,nBatch,actv){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

  #paramTrials<-paramTrials[sample(nrow(paramTrials), baselineTrials), ]

  # paramTrials<-unique.data.frame(paramTrials)
  #paramTrials<-readRDS("complexTrials.rds")
  for(i in 1:nrow(paramTrials)){
    #paramTrials<-readRDS("complexTrials.rds")  
    tempRes<-c()
    tempVal<-c()
    runTime<-c()

    for(data in klist){
      currentTime<-Sys.time() 
      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=ceiling(nrow(train)/paramTrials[i,]$nBatch)
      actv=paramTrials[i,]$actv
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/dsurv.py')

      ctrain<-train
      #ctrain$time<- train$time + runif(nrow(train),-0.000001,0.000001)

      coxnnsurv=fitDeepSurv(ctrain,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv)

      coxnnsurv<-t(coxnnsurv)
      cnnCleaned<-pyProcess(coxnnsurv,times=times)
      colnames(cnnCleaned)<-times
      py_run_string("del fitDeepSurv")
      rm(fitDeepSurv)

      miniee <- Score(list('mod'=cnnCleaned),
                      data =val, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      # coxnnsurv<-coxnnsurv[[1]]
      # coxnnsurv<-t(coxnnsurv)
      # #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
      # cnnCleaned<-pyProcess(coxnnsurv,times=times)
      # colnames(cnnCleaned)<-times#seq(0,1,length.out = ncol(cnnCleaned))
      # py_run_string("del fitDeepSurv")
      # rm(fitDeepSurv)
      # brierFinalResults <- Score(list('ds'=cnnCleaned),
      #                            data =as.data.frame(val),#rbind(train,val) 
      #                            formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
      #                            se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score
      # cutted<-brierFinalResults[which(brierFinalResults$model=="ds"),]
      #tempRes<-append(tempRes,mean(cutted[-c(1,2,24,25)]$IPA))
    }

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("prostateCV.rds")
test<-readRDS("prostateTest.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,test,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=FALSE,hide=FALSE}

optimDeepHit<-function(klist,test,times,baselineTrials,lr,drpt,layer1,layer2,nBatch,actv,alp){

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             alp=alp,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

  #paramTrials<-paramTrials[sample(nrow(paramTrials), baselineTrials), ]

  # paramTrials<-unique.data.frame(paramTrials)
  #paramTrials<-readRDS("complexTrials.rds")
  for(i in 1:nrow(paramTrials)){
    #paramTrials<-readRDS("complexTrials.rds")  
    tempRes<-c()
    tempVal<-c()
    runTime<-c()

    for(data in klist){
      currentTime<-Sys.time() 
      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      val<-normalizer(val,means,sds,maxTime)
      train<-normalizer(train,means,sds,maxTime)
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=ceiling(nrow(train)/paramTrials[i,]$nBatch)
      actv=paramTrials[i,]$actv
      alp=paramTrials[i,]$alp
      #=paramTrials[i,]$IPA
      #=paramTrials[i,]$valLoss
      source_python('src/deephitter.py')
      hitnnSurv=fitDeephit(train,val,bsize,epochs=epo,valida=val,patience=patience,min_delta=min_delta,drpt=drpt,lay1=layer1,lay2=layer2,lr=lr,actv=actv,alp=alp)
      hitnnSurv<-t(hitnnSurv)
      deephitCleaned<-pyProcess(hitnnSurv,times=times)
      colnames(deephitCleaned)<-times
      py_run_string("del fitDeephit")
      rm(fitDeephit)

      miniee <- Score(list('mod'=deephitCleaned),
                      data =val, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])
      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time() 
    }

    #paramTrials$IPA[i]<-mean(tempRes)
    #paramTrials$IPAse[i]<-sd(tempRes)
    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("prostateCV.rds")
test<-readRDS("prostateTest.rds")
times<-seq(from=min(test$time)+0.000001,
           to=max(test$time)-0.000001,
           length.out = 25
)

bestDH<-optimDeepHit(klist,test,times,baselineTrials=baselineTrials,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=FALSE,hide=FALSE}

optimCBNN<-function(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv){

  # 
  # for (i in 1:length(klist)){
  #   #train<-sampleCaseBase(data = as.data.frame(klist[[i]]$train),time="time",event="status",ratio=100)
  #   valcb<-sampleCaseBase(data = as.data.frame(klist[[i]]$val),time="time",event="status",ratio=100)
  #   valcbtensor<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
  #                          as.matrix(valcb[,ncol(valcb),drop=F])),
  #                     as.matrix(valcb[,ncol(valcb)-1,drop=F]))
  #   #valcbtensor[[1]][[2]]<-rep(train$offset[1],nrow(valcbtensor[[1]][[1]]))      
  #   #klist[[i]]$train<-train
  #   klist[[i]]$val<-valcbtensor
  # }

  paramTrials<-as.data.frame(tidyr::crossing(lr=lr,
                                             drpt=drpt,
                                             layer1=layer1,
                                             layer2=layer2,
                                             nBatch=nBatch,
                                             actv=actv,
                                             #IPA=NA,
                                             #IPAse=NA,
                                             valLoss=NA,
                                             runtime=NA))

  #paramTrials<-paramTrials[sample(nrow(paramTrials), 2), ]

  # paramTrials<-unique.data.frame(paramTrials)
  #paramTrials<-readRDS("complexTrials.rds")
  for(i in 1:nrow(paramTrials)){
    #paramTrials<-readRDS("complexTrials.rds")  
    tempRes<-c()
    tempVal<-c()
    runTime<-c()

    for(data in klist){

      train<-data$train
      val<-data$val
      maxTime<-max(train$time)
      sds<-sapply(train, function(x) (sd(x)))
      means<-sapply(train, function(x) (mean(x)))
      #val[[1]][[1]]<-as.matrix(normalizer(as.data.frame(val[[1]][[1]]),means,sds))
      train<-normalizer(train,means,sds,maxTime)

      #train[,ncol(train)]<-data$train[,ncol(train)]
      val<-normalizer(val,means,sds,maxTime)
      valTest<-val
      times<-seq(from=min(val$time),
                 to=max(val$time),
                 length.out = 22
      )

      train<-sampleCaseBase(data = as.data.frame(train),time="time",event="status",ratio=100)
      valcb<-sampleCaseBase(data = as.data.frame(val),time="time",event="status",ratio=100)
      val<-list(list(as.matrix(valcb[,-c(ncol(valcb)-1,ncol(valcb))]),
                     as.matrix(valcb[,ncol(valcb),drop=F])
      ),
      as.matrix(valcb[,ncol(valcb)-1,drop=F])
      )
      val[[1]][[2]]<-rep(train$offset[1],nrow(val[[1]][[1]]))
      #val[[1]][[2]]<-rep(0,nrow(val[[1]][[1]]))

      lr=paramTrials[i,]$lr
      drpt=paramTrials[i,]$drpt
      layer1=paramTrials[i,]$layer1
      layer2=paramTrials[i,]$layer2
      bsize=c(floor(nrow(train)/paramTrials[i,]$nBatch))
      actv=paramTrials[i,]$actv

      currentTime<-Sys.time()

      covars_input<-layer_input(shape=c(length(colnames(train))-2),
                                name = 'main_input')

      covars_output<-covars_input%>% 
        layer_dense(units=layer1,use_bias = T,activation = actv)%>%
        layer_dropout(drpt)%>%
        layer_dense(units=layer2,use_bias = T,activation = actv)%>%
        layer_dropout(drpt)%>%
        layer_dense(units=1,use_bias = T)

      fit<-fitSmoothHaz(cbnn,
                        epochs=epo,
                        batch_size=bsize,
                        verbose=0,
                        monitor="val_loss",
                        #val_split=0.2,
                        min_delta=min_delta,
                        patience=patience,val=val)
      #tempVal<-append(tempVal,min(fit$resultOfFit$metrics$val_loss))
      annPreds<-aar(fit,
                    times=times,
                    x_test=valTest[,-c(ncol(valTest))]
      )

      miniee <- Score(list('mod'=annProperpoly),
                      data =valTest, 
                      formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                      se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)$Brier$score

      tempVal<-append(tempVal,miniee$IBS[which(miniee$model=="mod" & miniee$times==max(miniee$times))])

      runTime<-append(runTime, Sys.time()-currentTime)
      currentTime<-Sys.time()

      rm(cbnn,fit,covars_input,covars_output)
    }

    paramTrials$valLoss[i]<-mean(tempVal)
    paramTrials$runtime[i]<-mean(runTime)
    #saveRDS(paramTrials,"complexds.rds")
    print(paste("trial",i,"out of ",nrow(paramTrials)))
    print(sum(runTime))
    #print(as.character(paramTrials[i,]))
    #rm(cbnn,fit,annPreds,covars_input,covars_output)
    gc()
  }
  bestPerformance<-paramTrials[which.min(paramTrials$valLoss),]
  return(bestPerformance)
}

klist<-readRDS("prostateCV.rds")
test<-readRDS("prostateTest.rds")

cbnnPerformance<-optimCBNN(klist,test,times,lr,drpt,layer1,layer2,nBatch,actv)

#cbnnPerformance<-cbnnPerformance[which.min(cbnnPerformance$valLoss),]

@@

```{r winners,eval=FALSE,hide=FALSE}
winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

#saveRDS(winners,"prostateWins.rds")

@@

winners<-readRDS("prostateWins.rds")

klist<-readRDS("prostateCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)
#data$time<-data$time/max(data$time)

@@

  fullTest<-readRDS("prostateTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  saveRDS(BrierIPAList,'results/100prostateBrier.rds')
  saveRDS(cScore,'results/100prostatecidx.rds')
  saveRDS(AUClist,'results/100prostateAuc.rds')
  pos=pos+1

>>>>

```{r setup, include=T}
set.seed(1)
knitr::opts_chunk$set(echo = TRUE)
source("src/packages.R")
source("src/functions.R")
library(reticulate)
eval_prostate<-T

source_python("src/cIndex.py")

##########################
###Shared Hyperparameters
##########################
#bsize=512
min_delta = 0 #10^-7

@@

```{r prostatePrep,eval=TRUE,hide=FALSE}

@@

#saveRDS(res$test,"cvData/prostateTest.rds")

@@

  g = sample(cut(
    seq(nrow(data)), 
    nrow(data)*cumsum(c(0,spec)),
    labels = names(spec)
  ))
  klist[[i]]= split(data, g)
}
#saveRDS(klist,"cvData/prostateCV.rds")

@@

```{r setFixedHyperparameters,eval=TRUE,hide=FALSE}

klist<-readRDS("cvData/prostateCV.rds")

@@

lr=c(0.01)
drpt=c(0.01)
layer1=c(50)
layer2=c(10)
nBatch=c(100)
actv=c("relu","linear")#
alp=c(0)

@@

```{r hyperOpDsurv,eval=TRUE,hide=FALSE}

klist<-readRDS("cvData/prostateCV.rds")
source_python('src/dsurv.py')
bestDS<-optimDeepSurv(klist,lr,drpt,layer1,layer2,nBatch,actv)

@@

```{r optimDeepHit,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/prostateCV.rds")
bestDH<-optimDeepHit(klist,lr,drpt,layer1,layer2,nBatch,actv,alp)

@@

```{r hyperopcbnn,eval=TRUE,hide=FALSE}
klist<-readRDS("cvData/prostateCV.rds")
cbnnPerformance<-optimCBNN(klist,lr,drpt,layer1,layer2,nBatch,actv)

```{r winners,eval=TRUE,hide=FALSE}

winners<-list(cbnn=cbnnPerformance,
              ds=bestDS,
              dh=bestDH)

#saveRDS(winners,"cvData/prostateWins.rds")

@@

winners<-readRDS("cvData/prostateWins.rds")

klist<-readRDS("cvData/prostateCV.rds")
data<-rbind(klist[[1]]$train,klist[[1]]$val)

@@

  fullTest<-readRDS("cvData/prostateTest.rds")
  test<-fullTest[,-c(ncol(data))]
  test<-normalizer(fullTest,means,sds,maxTime)[,-c(ncol(data))]
  fullTest<-normalizer(fullTest,means,sds,maxTime)

@@

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )
  print(paste("current iter:",pos))
  #saveRDS(BrierIPAList,'results/100prostateBrier.rds')
  #saveRDS(cScore,'results/100prostatecidx.rds')
  #saveRDS(AUClist,'results/100prostateAuc.rds')
  pos=pos+1
